The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multiphase Forest Inventories

### 2017-08-18 rnw/Analysis and Visualization.Rnw
update Andreas 18.08.2017(2)

The structure of an \code{esttable} object is very similar to the objects created by the small area estimation functions of the package. However, the point estimates, variances from all estimation objects passed to \code{estTable()} have been stored in one single column (\code{estimate} and \code{variance}) and can be distinguished by the variables \code{method}, \code{estimator} and \code{vartype} which specify the estimation method (one, two or threephase), the estimator and the type of variance (\code{g_} for \textit{g-weight} and \code{ext_} for \textit{external} variance) that was applied. Note that per default, also the confidence intervals are added.

@@

% Interpretation: (gain and rel.eff)
The function call returns a data frame containing the one-phase variance (\code{var_onephase}) and the variance of the best performing multi-phase estimator (\code{var_multiphase}). The multi-phase estimation procedure is again specified in the \code{method} and \code{estimator} column. The last two columns then actually quantify the potential benefit of the multi-phase estimation. The \code{gain} is the reduction (if its value is positive) or possibly also the increase (if its value is negative) in variance when applying the multi-phase as alternative to the onephase estimation. For small area \code{"B"}, it can be read as "the \textit{twophase extended psynth} estimation procedure leads to a 67.9 \% reduction in variance compared to the onephase procedure". The column \code{rel.eff} specifies the \textbf{\textit{relative efficiency}} which is defined as the ratio between the one-phase variance and the multi-phase variance:

@@

The \textit{relative efficiency} can be interpreted as the relative sample size of the one-phase estimator needed to achieve the variance of the multi-phase estimator. For small area \code{"B"} we can thus see that we would have to increase the terrestrial sample size by factor 3 in order to get the same estimation precision with the one-phase approach as using the \textit{twophase extended psynth} estimator. If the average costs for a terrestrial sample plot survey are known, the relative efficiency can thus be a simple mean of quantifying the financial benefit of multi-phase forest inventories.

>>>>

The structure of an \code{esttable} object is very similar to the objects created by the small area estimation functions of the package. However, the point estimates and variances from all estimation objects passed to \code{estTable()} have been stored in one single column (\code{estimate} and \code{variance}) and can be distinguished by the variables \code{method}, \code{estimator} and \code{vartype} which specify the estimation method (one, two or threephase), the estimator and the type of variance (\code{g_} for \textit{g-weight} and \code{ext_} for \textit{external} variance) that was applied. Per default, also the confidence intervals are added.

@@

% Interpretation: (gain and rel.eff)
The function call returns a data frame containing the one-phase variance (\code{var_onephase}) and the variance of the best performing multi-phase estimator (\code{var_multiphase}). The multi-phase estimation procedure is again specified in the \code{method} and \code{estimator} column. The last two columns then actually quantify the potential benefit of the multi-phase estimation. The \code{gain} is the reduction (if its value is positive) or possibly also the increase (if its value is negative) in variance when applying the multi-phase as alternative to the one-phase estimation. For small area \code{"B"}, it can be read as "the \textit{twophase extended psynth} estimation procedure leads to a 67.9 \% reduction in variance compared to the one-phase procedure". The column \code{rel.eff} specifies the \textbf{\textit{relative efficiency}} which is defined as the ratio between the one-phase variance and the multi-phase variance:

@@

The \textit{relative efficiency} can be interpreted as the relative sample size of the one-phase estimator needed to achieve the variance of the multi-phase estimator. For small area \code{"B"} we can thus see that we would have to increase the terrestrial sample size by factor 3 in the one-phase approach in order to get the same estimation precision as the \textit{twophase extended psynth} estimator. If the average costs for a terrestrial sample plot survey are known, the relative efficiency can thus be a simple mean of quantifying the financial benefit of multi-phase forest inventories.
